Supplements for the manuscript `Variation in gaze following across the life span: A process-level perspective'

### 2024-03-27 stats/gazemodel.Rmd
prepare revision

saveRDS(dev_plot, file = "../saves/gazemodel_dev_plot.rds")

@@

saveRDS(model_vs_data_plot, file = "../saves/gazemodel_model_vs_data.rds")

# ggsave("../figures/gazemodel_model_vs_data.png", width = 8, height = 5, scale = 1, bg = "white")
# ggsave("../figures/gazemodel_model_vs_data.pdf", width = 8, height = 5, scale = 1, bg = "white")
```

@@

faceted_inf
saveRDS(faceted_inf, "../saves/supplements_gazemodel_facetedinference.rds")

@@

# saveRDS(ind_sd_long, file = "../saves/gazemodel_ind_sd_long.rds")
# ind_sd_long <- readRDS("../saves/gazemodel_ind_sd_long.rds")

@@

saveRDS(priorMode, file = "../saves/gazemodel_prior.rds")

@@

# gen_model_clicks <- ind_sd_long %>%
#   rowwise() %>%
#   mutate(modelClick = get_click_prior(
#           sdTol = sdTol,
#           eyeCenterLY = eyeCenterLY,
#           eyeCenterLX = eyeCenterLX, 
#           eyeCenterRY = eyeCenterRY,
#           eyeCenterRX = eyeCenterRX,
#           targetCenterX = targetCenterX,
#           pupilLX = pupilLX,
#           pupilRX = pupilRX,
#           targetCenterY = targetCenterY,
#           priorInt = priorMode %>% filter(type == "intercept") %>% pull(mode),
#           priorSlope = priorMode %>% filter(type == "slope") %>% pull(mode),
#           age = age
#           ))
# 
# modelpred_gaze <- gen_model_clicks %>%
#   mutate(
#     modelClickDist = abs(modelClick - targetCenterX),
#     targetBin = cut(targetCenterX, 
#                     breaks = seq(from = 0, to = 1920, by = 192),
#                     labels = as.character(1:10))
#   ) %>%
#   group_by(age_group, targetBin) %>%
#   summarise(
#     data_mean = mean(clickDist) / 160, 
#     model_mean = mean(modelClickDist) / 160,
#   )

# saveRDS(modelpred_gaze, "../saves/gazemodel_modelpred_gaze.rds")
modelpred_gaze <- readRDS("../saves/gazemodel_modelpred_gaze.rds")

u_data <- full_join(modelpred_gaze, model_adults_bins)
saveRDS(u_data, "../saves/gazemodel_u_data.rds")

@@

u_plot
saveRDS(u_plot, "../saves/gazemodel_u_plot.rds")
# ggsave("../figures/gazemodel_Uplot.png", width = 8, height = 5, scale = 1, bg = "white")
# ggsave("../figures/gazemodel_Uplot.pdf", width = 8, height = 5, scale = 1, bg = "white")
```

```{r modelpred_gaze_plot}
# correlation model predicted imprecision vs data imprecision across target positions
modelpred_gaze_plot <- modelpred_gaze %>% 
  ggplot(., aes(x = model_mean, y = data_mean)) +
  geom_point(aes(col = targetBin)) +
  stat_cor(method = "pearson", label.x = 0.2, label.y = 4.9, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") +
  geom_abline(intercept = 0, slope = 1, linetype = 3) +
  scale_color_brewer(palette="BrBG") +
  labs(x = "Mean predicted imprecision", y = "Mean data imprecision", color = "Target bin") + 
  scale_x_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1)) + 
  scale_y_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1))

@@

# corr plot
modelpred_center_plot <- modelpred_center %>% 
  ggplot(., aes(x = model_mean, y = data_mean)) +
  geom_point(aes(col = targetBin), size = 0.8) +
  stat_cor(method = "pearson", label.x = 0.2, label.y = 4.9, aes(label = paste(..r.label..)), size = 3, r.accuracy = 0.01, cor.coef.name = "r") +
  geom_abline(intercept = 0, slope = 1, linetype = 3) +
  scale_color_brewer(palette="BrBG") +
  labs(x = "Mean predicted imprecision", y = "Mean data imprecision", color = "Target bin") + 
  scale_x_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1)) + 
  scale_y_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1))

@@

# corr plot
modelpred_random_plot <- modelpred_random %>% 
  ggplot(., aes(x = model_mean, y = data_mean)) +
  geom_point(aes(col = targetBin), size = 0.8) +
  stat_cor(method = "pearson", label.x = 0.2, label.y = 4.9, aes(label = paste(..r.label..)), size = 3, r.accuracy = 0.01, cor.coef.name = "r") +
  geom_abline(intercept = 0, slope = 1, linetype = 3) +
  scale_color_brewer(palette="BrBG") +
  labs(x = "Mean predicted imprecision", y = "Mean data imprecision", color = "Target bin") + 
  scale_x_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1)) + 
  scale_y_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1))

@@

  modelpred_gaze_plot + 
    theme(legend.position = c(0.85, 0.3), 
          legend.title = element_text(size = 8),
          legend.text = element_text(size = 8), 
          legend.box.background = element_rect(), 
          legend.key.height = unit(0.3, "cm"),
          legend.key.width = unit(-1.5, "cm"),
          plot.margin = margin(0.2, -2, 0.1, 0.2, "cm") # t r b l
         ),

@@

@@

```{r get_dist}
# get_dist <- function(sdTol, eyeCenterLY, eyeCenterLX, eyeCenterRY, eyeCenterRX, targetCenterY, targetCenterX, pupilLX, pupilRX){
# 
#   if(eyeCenterLX > pupilLX) {
#     tAlphaL = atan(abs(eyeCenterLX-targetCenterX)/(eyeCenterLY-targetCenterY))
#   } else {
#     tAlphaL = -atan(abs(eyeCenterLX-targetCenterX)/(eyeCenterLY-targetCenterY))
#   }
#   
#   #noisyAlphaL = rnorm(1,tAlphaL, sdPer)
#   
#   if(eyeCenterRX > pupilRX) {
#     tAlphaR = atan(abs(eyeCenterRX-targetCenterX)/(eyeCenterRY-targetCenterY))
#   } else {
#     tAlphaR = -atan(abs(eyeCenterRX-targetCenterX)/(eyeCenterRY-targetCenterY))
#   }
#   
#   #noisyAlphaR = rnorm(1,tAlphaR, sdPer)
# 
#   bRDist = c()
#   
#   bLDist = c()
#   
#   for (x in 1:1920){
#     
#   if(eyeCenterLX > x) {
#     betaL = atan(abs(eyeCenterLX-x)/(eyeCenterLY-targetCenterY))
#   } else {
#     betaL = -atan(abs(eyeCenterLX-x)/(eyeCenterLY-targetCenterY))
#   }
#     betaLDist = dnorm(betaL,tAlphaL,sdTol, log = T)
#     
#   if(eyeCenterRX > x) {
#     betaR = atan(abs(eyeCenterRX-x)/(eyeCenterRY-targetCenterY))
#   } else {
#     betaR = -atan(abs(eyeCenterRX-x)/(eyeCenterRY-targetCenterY))
#   }
#     betaRDist = dnorm(betaR,tAlphaR,sdTol, log = T)
#     
#     #betaDist = betaLDist + betaRDist
#     
#     #bDist[x] <- exp(betaDist)
#     bRDist[x] <- betaRDist
#     
#     bLDist[x] <- betaLDist
#     
#   }
#   
#   xRDist = exp(bRDist-logSumExp(bRDist))
#   
#   xLDist = exp(bLDist-logSumExp(bLDist))
#   
#   xDist = xRDist * xLDist
#   
#   dist = xDist / sum(xDist)
#   
#   # click = sample(1:1920, prob = xDist, size = 1)-1
#   
#   return(dist)
# }
```

```{r headlight_dist}
# headlight_df <- data.frame(
#   coord = 1:1920,
#   sdTol = "0.175"
# )
# 
# for (i in c(960,1736)){
#   
#   probdist <-  get_dist(
#     sdTol = 0.175,
#     targetCenterX = i,
#     eyeCenterLY = 937.8,
#     eyeCenterLX = 872.12,
#     eyeCenterRY = 937.8,
#     eyeCenterRX = 1045.89,
#     targetCenterY = 127.5,
#     pupilLX = i-1,
#     pupilRX = i-1)
#   
#     colname = as.character(i)
#     
#     headlight_df[, colname] <- probdist
#   
#   }
# 
# headlight_df %>%
#   pivot_longer(names_to = "target_coordinate", values_to = "probability", cols = c(-coord, -sdTol)) %>%
#   filter(target_coordinate == "960") %>%
#   ggplot(aes(x = coord, y = probability, group = interaction(target_coordinate,sdTol))) +
#   geom_density(stat = "identity", color = "blue", fill = "blue", alpha = .5) +
#   ylim(0, 0.006) +
#   scale_x_continuous(limits = c(0, 1920), breaks = seq(0, 1920, 480)) +
#   guides(fill = F) + 
#   # geom_vline(aes(xintercept = as.numeric(target_coordinate)), lty = 2, alpha = .25) +
#   # labs(x = "Coordinate", y = "Probability") +
#   # scale_fill_colorblind(name = "Inference SD") +
#   theme_few() + 
#   theme(
#     panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
#     panel.grid.minor = element_blank(), 
#     panel.grid.major = element_blank(),
#     plot.background = element_rect(fill = "transparent",colour = NA)
# )
# 
# ggsave("../figures/gazemodel_headlight_dist_side.png", width = 15, height = 4, bg = "transparent")
# 
# ##  Standard normal dist
# dnorm_one_sd <- function(x){
#   norm_one_sd <- dnorm(x)
#   # Have NA values outside interval x in [-1, 1]:
#   norm_one_sd[x <= -1 | x >= 1] <- NA
#   return(norm_one_sd)
# }
# 
# ggplot(data.frame(x = c(-4, 4)), aes(x = x)) +
#   stat_function(fun = dnorm, color = "darkgrey", linewidth = 2) + 
#   stat_function(fun = dnorm_one_sd, geom = "area", fill = "blue", alpha = 0.5) +
#   # geom_vline(aes(xintercept = 0), lty = 2, color = "blue") +
#   theme_void()
# 
# ggsave("../figures/gazemodel_normal_dist.png", width = 10, height = 4)
```

>>>>

saveRDS(dev_plot, file = "../saves/gazemodel_dev_plot.rds")
dev_plot <- readRDS("../saves/gazemodel_dev_plot.rds")

@@

saveRDS(model_vs_data_plot, file = "../saves/gazemodel_model_vs_data.rds")
model_vs_data_plot <- readRDS("../saves/gazemodel_model_vs_data.rds")
# ggsave("../figures/gazemodel_model_vs_data.png", width = 8, height = 5, scale = 1, bg = "white")
# ggsave("../figures/gazemodel_model_vs_data.pdf", width = 8, height = 5, scale = 1, bg = "white")
```

@@

faceted_inf
saveRDS(faceted_inf, "../saves/supplements_gazemodel_facetedinference.rds")
faceted_inf <- readRDS("../saves/supplements_gazemodel_facetedinference.rds")

@@

saveRDS(ind_sd_long, file = "../saves/gazemodel_ind_sd_long.rds")
# ind_sd_long <- readRDS("../saves/gazemodel_ind_sd_long.rds")

@@

saveRDS(priorMode, file = "../saves/gazemodel_prior.rds")
# priorMode <- readRDS("../saves/gazemodel_prior.rds")

@@

gen_model_clicks <- ind_sd_long %>%
  rowwise() %>%
  mutate(modelClick = get_click_prior(
          sdTol = sdTol,
          eyeCenterLY = eyeCenterLY,
          eyeCenterLX = eyeCenterLX,
          eyeCenterRY = eyeCenterRY,
          eyeCenterRX = eyeCenterRX,
          targetCenterX = targetCenterX,
          pupilLX = pupilLX,
          pupilRX = pupilRX,
          targetCenterY = targetCenterY,
          priorInt = priorMode %>% filter(type == "intercept") %>% pull(mode),
          priorSlope = priorMode %>% filter(type == "slope") %>% pull(mode),
          age = age
          ))

saveRDS(gen_model_clicks, file = "../saves/gazemodel_gen_model_clicks.rds")
# gen_model_clicks <- readRDS("../saves/gazemodel_gen_model_clicks.rds")

modelpred_gaze <- gen_model_clicks %>%
  mutate(
    modelClickDist = abs(modelClick - targetCenterX),
    targetBin = cut(targetCenterX,
                    breaks = seq(from = 0, to = 1920, by = 192),
                    labels = as.character(1:10))
  ) %>%
  group_by(age_group, targetBin) %>%
  summarise(
    data_mean = mean(clickDist) / 160,
    model_mean = mean(modelClickDist) / 160,
  )

saveRDS(modelpred_gaze, "../saves/gazemodel_modelpred_gaze.rds")
modelpred_gaze <- readRDS("../saves/gazemodel_modelpred_gaze.rds")

u_data <- full_join(modelpred_gaze, model_adults_bins)
saveRDS(u_data, "../saves/gazemodel_u_data.rds")
# u_data <- readRDS("../saves/gazemodel_u_data.rds")

@@

u_plot
saveRDS(u_plot, "../saves/gazemodel_u_plot.rds")
u_plot <- readRDS("../saves/gazemodel_u_plot.rds")

# ggsave("../figures/gazemodel_Uplot.png", width = 8, height = 5, scale = 1, bg = "white")
# ggsave("../figures/gazemodel_Uplot.pdf", width = 8, height = 5, scale = 1, bg = "white")
```

```{r modelpred_gaze_plot}
# correlation model predicted imprecision vs data imprecision across target positions
modelpred_gaze_plot <- modelpred_gaze %>% 
  ggplot(., aes(x = model_mean, y = data_mean)) +
  geom_point(aes(col = targetBin, shape = as.factor(age_group))) +
  stat_cor(method = "pearson", label.x = 0.2, label.y = 4.9, aes(label = paste(..r.label..)), size = 4, r.accuracy = 0.01, cor.coef.name = "r") +
  geom_abline(intercept = 0, slope = 1, linetype = 3) +
  scale_color_brewer(palette="BrBG") +
  labs(x = "Mean predicted imprecision", y = "Mean data imprecision", color = "Target bin", shape = "Age group") + 
  scale_x_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1)) + 
  scale_y_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1))

@@

# corr plot
modelpred_center_plot <- modelpred_center %>% 
  ggplot(., aes(x = model_mean, y = data_mean)) +
  geom_point(aes(col = targetBin, shape = as.factor(age_group)), size = 0.8) +
  stat_cor(method = "pearson", label.x = 0.2, label.y = 4.9, aes(label = paste(..r.label..)), size = 3, r.accuracy = 0.01, cor.coef.name = "r") +
  geom_abline(intercept = 0, slope = 1, linetype = 3) +
  scale_color_brewer(palette="BrBG") +
  labs(x = "Mean predicted imprecision", y = "Mean data imprecision", color = "Target bin", shape = "Age group") + 
  scale_x_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1)) + 
  scale_y_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1))

@@

# corr plot
modelpred_random_plot <- modelpred_random %>% 
  ggplot(., aes(x = model_mean, y = data_mean)) +
  geom_point(aes(col = targetBin, shape = as.factor(age_group)), size = 0.8) +
  stat_cor(method = "pearson", label.x = 0.2, label.y = 4.9, aes(label = paste(..r.label..)), size = 3, r.accuracy = 0.01, cor.coef.name = "r") +
  geom_abline(intercept = 0, slope = 1, linetype = 3) +
  scale_color_brewer(palette="BrBG") +
  labs(x = "Mean predicted imprecision", y = "Mean data imprecision", color = "Target bin", shape = "Age group") + 
  scale_x_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1)) + 
  scale_y_continuous(limits = c(0, 5.5), breaks = seq(0, 5, 1))

@@

  modelpred_gaze_plot + 
    theme(legend.position = c(0.85, 0.38), 
          legend.title = element_text(size = 6),
          legend.text = element_text(size = 6), 
          legend.box.background = element_rect(), 
          legend.key.height = unit(0.28, "cm"),
          legend.key.width = unit(-1.8, "cm"),
          plot.margin = margin(0.2, -2, 0.1, 0.2, "cm") # t r b l
         ),

@@

```{r get_click_motornoise}
get_click_motornoise <- function(targetCenterX){
  xDist = dnorm(seq(1:1920), mean = targetCenterX, sd = 160)

```{r get_click_linetracing}
get_click_linetracing <- function(targetCenterX){
  return(targetCenterX)
}
```

@@

```{r get_dist}
get_dist <- function(sdTol, eyeCenterLY, eyeCenterLX, eyeCenterRY, eyeCenterRX, targetCenterY, targetCenterX, pupilLX, pupilRX){

  xDist = xRDist * xLDist

  # click = sample(1:1920, prob = xDist, size = 1)-1

  return(dist)
}
```

```{r headlight_dist}
headlight_df <- data.frame(
  coord = 1:1920,
  sdTol = "0.175"
)

for (i in c(960,1736)){

  probdist <-  get_dist(
    sdTol = 0.175,
    targetCenterX = i,
    eyeCenterLY = 937.8,
    eyeCenterLX = 872.12,
    eyeCenterRY = 937.8,
    eyeCenterRX = 1045.89,
    targetCenterY = 127.5,
    pupilLX = i-1,
    pupilRX = i-1)

    colname = as.character(i)

    headlight_df[, colname] <- probdist

headlight_df %>%
  pivot_longer(names_to = "target_coordinate", values_to = "probability", cols = c(-coord, -sdTol)) %>%
  filter(target_coordinate == "1736") %>%
  ggplot(aes(x = coord, y = probability, group = interaction(target_coordinate,sdTol))) +
  geom_density(stat = "identity", color = "blue", fill = "blue", alpha = .5) +
  ylim(0, 0.006) +
  scale_x_continuous(limits = c(0, 1920), breaks = seq(0, 1920, 480)) +
  guides(fill = F) +
  # geom_vline(aes(xintercept = as.numeric(target_coordinate)), lty = 2, alpha = .25) +
  # labs(x = "Coordinate", y = "Probability") +
  # scale_fill_colorblind(name = "Inference SD") +
  theme_few() +
  theme(
    panel.background = element_rect(fill = "transparent",colour = NA), # or theme_blank()
    panel.grid.minor = element_blank(),
    panel.grid.major = element_blank(),
    plot.background = element_rect(fill = "transparent",colour = NA)
)

ggsave("../figures/gazemodel_headlight_dist_side.png", width = 15, height = 4, bg = "transparent")

##  Standard normal dist
dnorm_one_sd <- function(x){
  norm_one_sd <- dnorm(x)
  # Have NA values outside interval x in [-1, 1]:
  norm_one_sd[x <= -1 | x >= 1] <- NA
  return(norm_one_sd)
}

ggplot(data.frame(x = c(-4, 4)), aes(x = x)) +
  stat_function(fun = dnorm, color = "darkgrey", linewidth = 2) +
  stat_function(fun = dnorm_one_sd, geom = "area", fill = "blue", alpha = 0.5) +
  # geom_vline(aes(xintercept = 0), lty = 2, color = "blue") +
  theme_void()

ggsave("../figures/gazemodel_normal_dist.png", width = 10, height = 4)
```

# Simulated clicks from alternative models

```{r simulated_data}
simulated_data <- gen_model_clicks %>% 
  ungroup() %>%
  mutate(
    model_dist = modelClick - targetCenterX,
  ) %>%
  rename(target_center_x = targetCenterX) %>%
  group_by(id, trial_nr, target_center_x) %>% 
  summarize(
    gazemodel_click = mean(modelClick),
    gazemodel_dist = mean(model_dist),
  ) %>% 
  mutate(
    # line_click = target_center_x,
    linetracing_click = get_click_linetracing(target_center_x),
    linetracing_dist = linetracing_click - target_center_x, # = 0

    # motornoise_click = rnorm(n = n(), mean = target_center_x, sd = 160) %>% round(digits = 2),
    motornoise_click = get_click_motornoise(target_center_x),
    motornoise_dist = motornoise_click - target_center_x,

    # random_click = runif(n = n(), min = 0, max = 1920) %>% round(digits = 2), 
    random_click = get_click_random(),
    random_dist = random_click - target_center_x,

    # center_click = rnorm(n = n(), mean = 960, sd = 160) %>% round(digits = 2),
    center_click = get_click_center(),
    center_dist = center_click - target_center_x,
  )

simulated_data <- tango_kids %>% 
  select(subj_id, age, age_group, trial_nr, target_position, target_center_x, click_scaled_x, click_dist_from_target_center_x) %>% 
  rename(data_click = click_scaled_x, data_dist = click_dist_from_target_center_x) %>% 
  full_join(simulated_data, by = c("subj_id" = "id", "trial_nr", "target_center_x"))

simulated_wide <- simulated_data

simulated_mean <- simulated_data %>% 
    group_by(target_position) %>%
  summarise(
    data_click = mean(data_click), 
    gazemodel_click = mean(gazemodel_click),
    linetracing_click = mean(linetracing_click),
    motornoise_click = mean(motornoise_click),
    random_click = mean(random_click),
    center_click = mean(center_click),

    data_dist = mean(abs(data_dist)), 
    gazemodel_dist = mean(abs(gazemodel_dist)),
    motornoise_dist = mean(abs(motornoise_dist)),
    linetracing_dist = mean(abs(linetracing_dist)),
    random_dist = mean(abs(random_dist)),
    center_dist = mean(abs(center_dist)),
  ) %>% 
    pivot_longer(
    cols = -target_position,
    names_to = c("model", ".value"),
    names_sep = "_"
  ) %>% 
  mutate(
    model = factor(model, levels = c("data", "gazemodel", "linetracing", "motornoise", "random", "center"), labels = c("Data", "Gaze model", "Line-of-Sight", "LoS w. motor noise", "Random guessing", "Center bias")), 
  )

simulated_data <- simulated_data %>% 
  pivot_longer(
    cols = -c(subj_id, age, age_group, trial_nr, target_position, target_center_x),
    names_to = c("model", ".value"),
    names_sep = "_"
  ) %>%
  mutate(
    model = factor(model, levels = c("data", "gazemodel", "linetracing", "motornoise", "random", "center"), labels = c("Data", "Gaze model", "Line-of-Sight", "LoS w. motor noise", "Random guessing", "Center bias")), 
  )

saveRDS(simulated_data, file = "../saves/gazemodel_simulated_data.rds")
```

```{r simulated_data_plot}
sim_u <- simulated_mean %>% 
  ggplot(aes(x = target_position, y = dist, col = model, group = model)) +
  geom_point(alpha = 0.8, size = 1.5) +
  geom_line(alpha = 0.2) +
  scale_y_continuous(limits = c(0, 1920), breaks = seq(0, 1920, 320)) +
  labs(x = "Target bin", y = "Imprecision", col = "Source") + 
  scale_colour_viridis_d() +
  theme_minimal()

sim_cor <- simulated_wide %>% 
  group_by(age_group, target_position) %>%
  summarise(
    data = mean(abs(data_dist)),
    gazemodel = mean(abs(gazemodel_dist)),
    linetracing = mean(abs(linetracing_dist)),
    motornoise = mean(abs(motornoise_dist)),
    random = mean(abs(random_dist)),
    center = mean(abs(center_dist)),
  ) %>% 
  pivot_longer(cols = c(gazemodel, linetracing, motornoise, random, center), names_to = "model", values_to = "mean") %>% 
  mutate(
    model = factor(model, levels = c("gazemodel", "linetracing", "motornoise", "random", "center"), labels = c("Gaze model", "Line-of-Sight", "LoS w. motor noise", "Random guessing", "Center bias")), 
  ) %>% 
  ggplot(aes(x = mean, y = data)) +
  geom_point(aes(color = target_position, shape = as.factor(age_group)), alpha = 0.8, size = 0.8) +
  stat_cor(method = "pearson", label.x = 100, label.y = 960, aes(label = paste(..r.label..)), r.accuracy = 0.01, cor.coef.name = "r", size = 2.7, color = "black") +
  geom_abline(intercept = 0, slope = 1, linetype = 3) +
  labs(x = "Predicted imprecision", y = "Observed imprecision", color = "Target position", shape = "Age group") +
  scale_color_brewer(palette="BrBG") +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0, 960, 320)) +
  scale_y_continuous(limits = c(0, 1000), breaks = seq(0, 960, 320)) +
  facet_wrap(~model) + 
  theme_minimal() +
  theme(axis.title = element_text(size = 6), 
        axis.text = element_text(size = 6), 
        strip.text = element_text(size = 7), 
        legend.title = element_text(size = 6),
        legend.text = element_text(size = 6), 
        legend.key.height = unit(0.3, "cm"),
        legend.key.width = unit(-1.5, "cm"),
        )
sim_cor

sim_click <- ggplot() +
  geom_point(data = simulated_data, aes(x = target_position, y = click, col = model), alpha = 0.2, size = 0.75) +
  geom_point(data = simulated_mean, aes(x = target_position, y = click, col = model), shape = 4, size = 2, stroke = 1.5) +
  geom_line(data = simulated_mean, aes(x = target_position, y = click, col = model, group = model)) +
  scale_y_continuous(limits = c(0, 1920), breaks = seq(0, 1920, 320)) +
  labs(x = "Target bin", y = "Click coordinate", col = "Source") + 
  scale_colour_viridis_d(guide = "none") +
  theme_minimal() + 
  facet_wrap(~ model, nrow = 1)

sim_arranged <- ggarrange(
  ggarrange(sim_u, sim_cor, ncol = 2, widths = c(1, 1), labels = c("A", "B")),

  sim_click,

  nrow = 2, 
  labels = c("", "C")
)

sim_arranged

ggsave("../figures/gazemodel_simulated_u.png", width = 9, height = 5, bg = "white")
```

```{r inward_clicks}
tango_kids %>% 
  mutate(
    dist = ifelse(target_center_x < 960, click_scaled_x - target_center_x, target_center_x - click_scaled_x),
  ) %>% 
  ggplot(aes(x = dist, y = target_position)) +
  geom_density_ridges() + 
  geom_point(stat = "summary", fun = "mean", shape = 4, size = 2.5, position = position_nudge(y = 0.1)) +
  geom_vline(xintercept = 0, lty = 2, alpha = .25) +
  scale_x_continuous(limits = c(-960, 1920), breaks = seq(-960, 1920, 320)) +
  labs(x = "Distance from target center (higher: inward)", y = "Target bin")

ggsave("../figures/gazemodel_inward_clicks.png", width = 8, height = 5, bg = "white", scale = 1.1)
```

### 2024-03-27 stats/magnet.Rmd
major edits in intro & discussion
prepare revision

@@

@@

@@

write.csv(model_results, "../saves/magnet_modelresults.csv", quote = F, row.names = F)
saveRDS(model_results, "../saves/magnet_modelresults.rds")

write.csv(mmagnet_perspective, "../saves/magnet_winningmodel.csv", quote = F, row.names = F)
saveRDS(mmagnet_perspective, "../saves/magnet_winningmodel.rds")
```

>>>>

```{r descriptives_table}
magnet_descriptives <- magnet_data %>% 
  select(-c(subj_id, gender, age_group, age, age_centered)) %>%
  describe() %>% 
  select(n, mean, sd, median, min, max)

magnet_descriptives
saveRDS(magnet_descriptives, "../saves/magnet_descriptives.rds")
```

@@

```{r explorative}
tango_tom_excl_perspective <- magnet_data %>% 
  group_by(subj_id) %>% 
  mutate(
    tom_excl_perspective = sum(desires, knowledge, content, explicit)
  ) %>% 
  ungroup() %>% 
  select(tango_mean, tom_excl_perspective) %>% 
  corr.test(method = "spearman")

tango_tom_excl_perspective$ci

tom_perspective <- magnet_data %>% 
  group_by(subj_id) %>% 
  mutate(
    tom_excl_perspective = sum(desires, knowledge, content, explicit)
  ) %>% 
  ungroup() %>% 
  select(perspective_aggregate, tom_excl_perspective) %>% 
  corr.test(method = "spearman")

tom_perspective$ci
```

@@

```{r cor_triallevel}
tango_trials <- read_csv("../data/magnet-tango-data.csv")
magnet_trials <- read_csv("../data/magnet-tablet-data.csv")

trials_bins <- tango_trials %>% 
  group_by(subj_id, target_position) %>%
  summarise(click_dist_tango = mean(click_dist_balloons, na.rm = T)) %>%

  full_join(magnet_trials %>% 
      rename(target_position = magnet_bin) %>%
      group_by(subj_id, target_position) %>%
      summarise(click_dist_magnet = mean(click_dist_magnets, na.rm = T)))

trials_bins

trials_bins_cor <- corr.test(trials_bins$click_dist_tango, trials_bins$click_dist_magnet, method = "pearson", use = "pairwise.complete.obs")

trials_bins_cor$ci

trials_bins_cov <- cov(trials_bins$click_dist_tango, trials_bins$click_dist_magnet, method = "pearson", use = "pairwise.complete.obs")
```

@@

write.csv(model_results, "../saves/magnet_modelresults.csv", quote = F, row.names = F)
saveRDS(model_results, "../saves/magnet_modelresults.rds")
model_results <- readRDS("../saves/magnet_modelresults.rds")

write.csv(mmagnet_perspective, "../saves/magnet_winningmodel.csv", quote = F, row.names = F)
saveRDS(mmagnet_perspective, "../saves/magnet_winningmodel.rds")
mmagnet_perspective <- readRDS("../saves/magnet_winningmodel.rds")
```

### 2024-03-27 supplements/supplements.Rmd
prepare revision

---
title             : "Supplements for the manuscript  'Variation in gaze understanding across the life span: A process-level perspective'"
shorttitle        : "Supplements"
author:

  - name          : "Julia Prein"
    affiliation   : "1"
  - name          : "Luke Maurits"
    affiliation   : "1"
  - name          : "Annika Werwach"
    affiliation   : "1"
  - name          : "Daniel B. M. Haun"
    affiliation   : "1,*"
  - name          : "Manuel Bohn"
    affiliation   : "1,2,*"
affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
  - id            : "2"
    institution   : "Institute of Psychology, Leuphana University Lüneburg, Germany"
  - id            : "*"
    institution   : "shared last authorship"  
floatsintext      : yes
bibliography      : ["../../references.bib"]
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa7"
classoption       : "man"
output            : papaja::apa6_pdf
header-includes:
  - \usepackage{setspace}
  - \usepackage{float}
  - \captionsetup[figure]{font={stretch=1}}
editor_options: 
  markdown: 
    wrap: sentence
---

@@

>>>>

---
title             : "Supplements for the manuscript  'Variation in gaze following across the life span: A process-level perspective'"
shorttitle        : "Supplements"
author:

  - name          : "Julia Prein"
    affiliation   : "1,2"
  - name          : "Luke Maurits"
    affiliation   : "1"
  - name          : "Annika Werwach"
    affiliation   : "1"
  - name          : "Daniel B. M. Haun"
    affiliation   : "1,*"
  - name          : "Manuel Bohn"
    affiliation   : "1,2,*"
affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
  - id            : "2"
    institution   : "Institute of Psychology, Leuphana University Lüneburg, Germany"
  - id            : "*"
    institution   : "shared last authorship"  
floatsintext      : yes
bibliography      : ["../../references.bib"]
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa7"
classoption       : "man"
output            : papaja::apa6_pdf
header-includes:
  - \usepackage{setspace}
  - \usepackage{float}
  - \captionsetup[figure]{font={stretch=1}}
editor_options: 
  markdown: 
    wrap: sentence
---

@@

## Simulations

In the manuscript, we have described the gaze model and two alternatives: random guessing and a center bias. Here, we consider two more alternatives. Let us consider a model that assumes participants can infer the agent’s focus without any noise (for example, by tracing the line of sight). A model like this would assume that participants follow gaze without any uncertainty. Therefore, no U curve would be predicted. 
Furthermore, let us assume another model in that participants still show no inferential noise, but they vary in their amount of motor noise, so how accurately participants then click at the corresponding location. A model like this would assume equal variance across the target locations, so we would not expect a U-shape here.

Please note that our random guessing model acts like 100% noise: the predictions of a participant’s click on a trial level range uniformly from 0 to 1920 (the whole screen range). The mean comes down to the center, namely 960. However, as you can see in the figure below, the U shape is weaker compared to the other models (Figure 1A). Most importantly, note that this is only the case when you average across all the trials. When you look at the individual trial-by-trial level, the models are defined by different data-generating processes, and therefore, their predictions differ, too (Figure 5C). In our correlational plots (Figure 5B), we see that the gaze model is clearly favored. This highlights the benefit that we gain through the modeling approach: even though a certain (U) pattern in the data could be elicited from several different models, we can disentangle which process is most likely causing this pattern.

(ref:figlab5) **Predictions of alternative models across target positions.** A: Predicted U-pattern across target positions by the different models. Note that this is averaged across trials and displays imprecision, i.e., the absolute distance between the target center and the click. B: Correlation between the predicted imprecision and the observed imprecision, by target position and age group. C: Predicted click coordinates (cf. not imprecision) by target position across the different models.

```{r fig5, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab5)"}
knitr::include_graphics("../figures/gazemodel_simulated_u.png")
```
